\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Joseph Petitti} & Email : \href{mailto:jppetitti@wpi.edu}{jppetitti@wpi.edu}\\
	\href{https://josephpetitti.com/}{https://josephpetitti.com} / \href{https://github.com/jojonium}{https://github.com/jojonium} & Phone : (518)-545-1984 \\
\end{tabular*}


%-----------OBJECTIVE-----------------
\section{Objective}
A summer 2019 internship in computer science

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Worcester Polytechnic Institute}{Worcester, MA}
      {Bachelor of Science in Computer Science;  GPA: 3.92/4.00}{Expec. May 2020}
    \resumeSubheading
      {Guilderland High School}{Guilderland, NY}
      {High School Diploma;  GPA: 4.0/4.0 }{June 2016}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C/C++, Javascript/JQuery, Java, PL/SQL, HTML/CSS, Python, Racket}
      \hfill
    }
    \item{
      \textbf{Technologies}{: GNU/Linux, Eclipse, IntelliJ IDEA, PyCharm, git, nginx, Microsoft Office}
      \hfill
    }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Worcester Polytechnic Institute}{Worcester, MA}
      {Teaching Assistant}{Aug 2018 - Present}
      \resumeItemListStart
        \resumeItem{Labs}
	  {Taught labs and graded assignments for undergraduate computer science classes at WPI.}
        \resumeItem{Office Hours}
	  {Held office hours weekly to assist students with programming concepts.}
      \resumeItemListEnd

    \resumeSubheading
      {MAPFRE Insurance}{Webster, MA}
      {Application Services Intern}{May 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem{Enterprise Web Appraisal System}
	  {The Enterprise Web Appraisal System (EWAS) is a web application developed by MAPFRE for internal use by their appraisers, automating the appraisal process and increasing efficiency and consistency. Worked on application services team to develop front-end and debug database.}
        \resumeItem{EWAS Front-End}
	  {Developed and deployed dynamic web application front-end in Javascript/JQuery.}
      \resumeItemListEnd

    \resumeSubheading
      {Guilderland High School Help Desk}{Guilderland, NY}
      {Student Technician}{Sep 2015 - Jun 2016}
      \resumeItemListStart
        \resumeItem{Information Technology Troubleshooting}
	  {Worked with a team of other students to fix information technology issues within the school.}
        \resumeItem{Hardware}
	  {Common work included setting up Chromebooks, repairing computers, fixing printers, servicing projectors, configuring network connections, and maintaining hardware inventories.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Personal Website}
      {Mar 2018 - Present. Independently designed and developed personal website to host projects. HTML, CSS, and Javascript on Ubuntu Server using nginx back-end.}
    \resumeSubItem{Operating Systems}
      {Aug - Oct 2018. Ubuntu Linux, C.}
    \resumeSubItem{Introduction to Machine Organization and Assembly Language}
      {Mar - Apr 2018. C, x86.}
    \resumeSubItem{Database Systems I}
      {Jan - Mar 2018. PL/SQL.}
    \resumeSubItem{Group Effort: Study Group Matching Service}
      {Aug - Dec 2016. Worked in group of four to research and create a web application to assign calculus students into study groups based on ability and availability.}
  \resumeSubHeadingListEnd


%-------------OTHER WORK HISTORY----------
\section{Work History}
  \resumeSubHeadingListStart
    \resumeSubItem{Wakpominee Scout Camp}
      {\textbf{Camp Counselor/Area Director}, Fort Ann, NY, Summer 2015 - 2017}
    \resumeSubItem{Beverwyck Senior Living Community}
      {\textbf{Wait Staff/Manager}, Slingerlands, NY, Jan 2015 - Jun 2017}
  \resumeSubHeadingListEnd

%--------AWARDS------------
\section{Awards/Other Positions}
  \resumeSubHeadingListStart
    \resumeSubItem{Risk Management Chairman}
      {Beta Theta Pi, Eta Tau Chapter, Jan 2018 - Present}
    \resumeSubItem{Charles O. Thompson Scholar}
      {WPI, Apr 2017}
    \resumeSubItem{Dean's List}
      {WPI, Fall 2016, Spring 2017, Fall 2017, Spring 2018}
    \resumeSubItem{National Merit Scholar Finalist}
      {GHS, 2016}
    \resumeSubItem{Eagle Scout Award}
      {Boy Scouts of America, Sep 2012}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
